%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TODO
	% dizer quantas publicações tenho em cada categoria
	% colocar a bold o meu nome


%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{article} % Document font size and paper size

\usepackage{fontspec} % Allows the use of OpenType fonts

\usepackage{geometry} % Allows the configuration of document margins
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in} % Document margin settings
\setlength\parindent{0in} % Remove paragraph indentation

\usepackage[usenames,dvipsnames]{xcolor} % Custom colors

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\reversemarginpar

\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Francisco Nunes - CV},pdfauthor={Francisco Nunes}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} % Link colors

\usepackage{eurosym}


%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Linux Libertine Font (default)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O} % Main text font
\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\sectionfont{\mdseries\upshape\Large} % Set font options for sections
\subsectionfont{\mdseries\scshape\normalsize} % Set font options for subsections
\subsubsectionfont{\mdseries\upshape\large} % Set font options for subsubsections
\chardef\&="E050 % Custom ampersand character

% Hoefler Text Font (bundled with Mac OSX)
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
%\setsansfont[Scale=0.9]{Optima Regular} % Set sans font, used in the main name and titles in the document
%\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}} % Custom ampersand character
%\sectionfont{\sffamily\mdseries\large\underline} % Set font options for sections
%\subsectionfont{\rmfamily\mdseries\scshape\normalsize} % Set font options for subsections
%\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} % Set font options for subsubsections

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

{\LARGE Francisco Nunes}\\[1cm] % Your name
% Rua Dr. Lopes Cardoso 505\\ % Your address
% 4420 Gondomar, Portugal\\[.2cm]
Born: December 20, 1987---Porto, Portugal\\ % Your date of birth
Nationality: Portuguese \& Brazilian \\% Your nationality

Email: \href{mailto:francisco.nunes@fraunhofer.pt}{francisco.nunes@fraunhofer.pt}\\ % Your email address
Personal page: \href{http://francisconunes.me}{http://francisconunes.me}\\
Scholar: \href{https://scholar.google.com/citations?user=D2rDc98AAAAJ}{https://scholar.google.com/citations?user=D2rDc98AAAAJ}\\
Twitter: \href{https://twitter.com/xico_nunes}{@xico\_nunes}

% \vfill % Whitespace between contact information and specific CV information

%------------------------------------------------



%------------------------------------------------

%\section*{Current position}

% \emph{PhD Student}, HCI Group, Vienna University of Technology % Your current or previous employment position

%------------------------------------------------

\section*{Research interests}

I am interested in learning about people and how they use technology. My projects are usually at the intersection of computer science, medicine, design, and social sciences. I am an expert in ethnographically informed design, user-centred design, and participatory design approaches.\\

Broad keywords for my work would be: Human-Computer Interaction, Computer-Supported Cooperative Work, Health Informatics, and Science and Technology Studies.


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section*{Education}

\years{2012-2017}\textsc{PhD} in Informatics (Human-Computer Interaction), TU Wien\\
\textit{Thesis: ``The Everyday Life with Parkinson's and Self-care Technologies"}\\
% Supervised by \\ Geraldine Fitzpatrick.}\\
\years{2005-2010}\textsc{MSc \& BSc} in Informatics and Computing Engineering, University of Porto\\
\textit{Thesis: ``Healthcare TV Based User Interfaces for Older Adults"}
 %Supervised by Teresa Galvão and Paula Alexandra Silva.}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section*{Experience}

\years{2017-now}Senior researcher, Fraunhofer Portugal AICOS, Porto\\
\years{2016-2017}Researcher, NOVA-LINCS, Universidade Nova de Lisboa, Lisboa\\ % 5/2016
\years{2012-2017}PhD Student, Institute for Design and Assessment of Technology, TU Wien, Vienna\\ % 9/2012
\years{2008-2012}Researcher, Fraunhofer Portugal AICOS, Porto \\% 9/2010--7/2012
%\years{2008-2010}Research Assistant, Fraunhofer Portugal AICOS, Porto % 7/2008--8/2010



%----------------------------------------------------------------------------------------
%	GRANTS, HONORS AND AWARDS SECTION
%----------------------------------------------------------------------------------------

\section*{Grants, honours \& awards}

\subsection*{Acquired project grants}
\years{2019}\euro117K - ``Demonstration of EyeFundusScope with Non-Expert Ophthalmology users'' funded by ANI (PT) -- \textit{Lead proposal writer and PI.}\\
\years{2011}\euro137K - ``Smartphones for Smart Seniors (S4S)" funded by ANI (PT) --  \textit{Lead proposal writer.}\\
\years{2011}\euro411k - ``Personal Health Device for the Remote and Autonomous Management of Parkinson's Disease (REMPARK)" funded by FP7-ICT (EU) -- \textit{Co-proposal writer.}\\
\years{*}\euro58K - Direct industry funding from Alcatel-Lucent \euro49k, Doist \euro9K.

\subsection*{Other grants and honours}
\years{2016}Two special recognitions for an `Excellent Review' at CHI 2016\\
%\years{2016}Grant for attending conference from TU Wien (\euro1390)\\
%\years{2015}Grant for attending CHI 2015 doctoral consortium (\$1300)\\
\years{2012}Vienna PhD School of Informatics scholarship (3 years of funding)\\
\years{2012}Dance! Don't Fall was on the Top-25 Apps, CES Mobile Apps Showdown\\
\years{2011}Smart Companion was 2nd most creative app, ZON Creativity Award (prize: \euro6250)\\
\years{2010}Mover was 5th best Lifestyle app, Android Developer Challenge II (prize: equipment)

\section*{Teaching \& supervision experience}

\subsection*{Courses}

\years{2019}Learning from Users: User Research Methods for Technology Design (MSc, PhD @AICOS)\\
\years{2016-2018}Qualitative methods and co-design of self-care technologies (MSc @U. of Copenhagen) -- \textit{Invited lecture on self-care and self-care technologies}\\
\years{2015}HCI in Healthcare (MSc @TU Wien) -- \textit{Co-teaching and project supervision}\\
\years{2014}User Research Methods (MSc @TU Wien)-- \textit{Co-teaching and project supervision}\\


\subsection*{Supervised students}

\years{ongoing}Niloufar Chakhmaghi, MSc Media Informatics @TU Wien\\
\years{2019}Jo\~{a}o Sim\~{o}es, MSc Biomedical Engineering @Universidade Nova de Lisboa\\
\years{2018}Cristiana Braga, MSc Service Design @FEUP\\
\years{2018}Jo\~{a}o Almeida, MSc Informatics Engineering @FEUP\\
\years{2015}Martin Herndl, BSc Medical Informatics @TU Wien\\
\years{2012}João Cevada, MSc Informatics Engineering @FEUP\\
\years{*}Other 8 students as unofficial MSc co-supervisor

% \years{ongoing}Niloufar Chakhmaghi, Co-design of web platform for Parkinson's consultations\\
% \years{2018}Cristiana Braga, Study of a self-management system for healthcare shiftworkers\\
% \years{2018}Jo\~{a}o Almeida, Restaurant recommendation system for people with food allergies\\
% \years{2015}Martin Herndl, Developing an Android Self-Management Application for People with Parkinson's Disease\\
% \years{2012}João Cevada, User Interface Design Recommendations for Fitting Smartphone Applications to Persons With Parkinson's\\

\subsection*{Supervised PhD internships}

\years{2019}Cristina Mendes Santos, PhD Internet Interventions @Link\"{o}ping University\\
\years{2018}Martina {\v C}ai\'c, PhD Service Design @Maastricht University\\


\section*{Projects}
% MASPARK
% DEM

\subsection*{Ongoing}

\years{2019-2021}\emph{EyeFundusScopeNEO} (PT2020) -- This project is piloting EyeFundusScope, a solution to screen diabetic retinopathy, in CUF Infante Santo. I am PI at AICOS.\\
\years{2016-2019}\emph{Physio@Home} (PT2020) -- This project is developing a solution to support physical rehabilitation for the home and clinic, using wearables and serious games. I am involved in the design and evaluation of the system; I also replaced the PI of the project for 14 months.\\


\subsection*{Selection of previous projects}

\years{2014-2018}\emph{Clockwork} (EU AAL-JP) -- This project developed technologies to support the self-care of shift workers. I was in charge of supervising the user research, design, and evaluation of the smartphone app and the smart badge, the tasks of AICOS. I also coordinated the project consortium for 24 months. \href{http://clockworkproject.eu/}{http://clockworkproject.eu/}\\
\years{2015-2018}\emph{MASPARK} (La Marat\'{o} de TV3) -- This project developed a system to detect and address freezing of gait in patients with Parkinson's. I was PI for 15 months, in charge of supervising the design and evaluation of the system.\\
% \years{2011-2015}\emph{REMPARK} (EU ICT-FP7) -- This project developed a wearable system to monitor symptoms of people with Parkinson's, intervene in the gait, and collect data to improve the therapy. I participated in the first year of the project and was involved in user research and early design phases of the smartphone apps for patients. \href{http://www.rempark.eu/}{http://www.rempark.eu/}\\
% 11/2011–07/2012
% \years{2011-2014}\emph{S4S} (ANI) -- This project adapted the Windows Phone for older adults. I participated in the first year of the project and was involved in the user research, design, and evaluation of some of the smartphone applications.\\
% 10/2011–07/2012
%\years{2011-2012}\emph{Dance! Don't Fall} (Internal) -- This project created an Android application that monitors the risk of falling while actively reducing it through dancing. I participated in the user research, design, and evaluation of the application. \href{http://dancedontfall.projects.fraunhofer.pt}{http://dancedontfall.projects.fraunhofer.pt}\\
\years{2010-2012}\emph{Smart Companion} (Internal) -- This project created an Android skin specifically designed for older people. I participated in the user research, design, and evaluation of the smartphone applications. Smart Companion is today being sold by GOCIETY under the name GOLIVEPHONE. \href{http://smartcompanion.projects.fraunhofer.pt}{http://smartcompanion.projects.fraunhofer.pt}\\
\years{2009-2012}\emph{eCAALYX} (EU AAL-JP) -- This project created a telehealth system for older adults with chronic conditions. I participated in the the user research, design, and evaluation of the TV interfaces for older adults. \href{http://ecaalyx.org}{http://ecaalyx.org}\\
% 06/2009–07/2012
% \years{2009-2012}\emph{Mover} (Internal) -- This project created an Android app that explored the accelerometer to capture activity and thus promote movement. I participated in the design and evaluation of the app. Mover is today being sold as part of the GOLIVEPHONE mentioned above. \href{http://mover.projects.fraunhofer.pt/}{http://mover.projects.fraunhofer.pt/}


\section*{Service}

\subsection*{Program committee member}

CHI 2020, 2019\\
CSCW 2018\\
PervasiveHealth 2015, 2016\\
Mindcare 2016\\
And in workshops at ICEC'18, CHI'16, GROUP '14, Ubicomp '13, and SouthCHI '13

% And several workshops:\\
% \years{2016}Advances in DIY Health \& Wellbeing at CHI '16\\
% \years{2014}Collaboration and Coordination in the Context of Informal Care Workshop at GROUP '14\\
% \years{2013}2nd Workshop on Computer Mediated Social Offline Interactions at Ubicomp '13\\
% \years{2013}Design Culture for Ageing Well Workshop at SouthCHI '13

\subsection*{Workshop organizer}

\years{2014}Designing Self-care for Everyday Life at NordiCHI '14 (\href{https://designingselfcareforeverydaylife.wordpress.com/}{link})\\
\years{2014}Designing Systems for Health and Entertainment: what are we missing? at ACE '14 (\href{https://designingsystemsforhealthandentertainment.wordpress.com/}{link})

\subsection*{Reviewer}

ENTCOM, Health Informatics Journal, IJCCI, IJHCS, IxD\&A, JAMIA, JCSCW, JMIR, TOCHI.\\
CHI ('19, '18, '17, '16, '15, '14), CSCW ('18, '17, '16, '15), DIS '18, Group '16, Healthcom '13, Interact '19, MobileHCI '17, NordiCHI ('16, '14), PervasiveHealth ('17, '16, '15).

\subsection*{Student volunteer}

CHI ('16, '13), CSCW '15 PC meeting, NordiCHI '10

\break




%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS SECTION
%----------------------------------------------------------------------------------------

\section*{Publications \& talks}

h-index: 12; citations: 438 (source Google Scholar as at 09/2019)

\subsection*{Proceedings and special issues edited}

\years{2016}P. A. Silva, F. Nunes, eds. (2016) ``Special issue on fun and engaging computing technologies for health'', \emph{Entertainment Computing}, 15: 41--70\\
\years{2015}N. Verdezoto, F. Nunes, E. Grönvall, G. Fitzpatrick, C. Storni, and M. Kyng, eds. (2015) ``Proceedings of Designing Self-care for Everyday Life. Workshop in conjunction with NordiCHI 2014, 27th October 2014, Helsinki, Finland'', \emph{DAIMI Report Series}, 41(597).\\
\years{2014}N. Verdezoto, F. Nunes, G. Fitzpatrick, and E. Grönvall, eds. (2014) ``Designing Self-Care For Everyday Life", \emph{Interaction Design and Architecture(s) Journal - IxD\&A}, 23: 142--190.

\subsection*{Journal articles}

\years{2017}F. Nunes, T. Andersen, and G. Fitzpatrick (2017) ``The agency of patients and carers in medical care and self-care technologies for interacting with doctors", \emph{Health Informatics Journal}, 1--20.\\
\years{2016}F. Güldenpfennig, F. Nunes, and G. Fitzpatrick (2016) ``Making Space to Engage: An Open-ended Exploration of Technology Design with Older Adults", \emph{International Journal of Mobile Human Computer Interaction}, 8(2): 1--19.\\
\years{2016}F. Nunes, P. A. Silva, J. Cevada, A. C. Barros, L. Teixeira (2015) ``User Interface Design Guidelines for Smartphone Applications for People With Parkinson's Disease", \emph{Universal Access in the Information Society}, 15(4): 659--679.\\
\years{2015}F. Nunes, N. Verdezoto, G. Fitzpatrick, M. Kyng, E. Grönvall, and C. Storni (2015) ``Self-care Technologies in HCI: Trends, Tensions, and Opportunities", \emph{ACM Transactions on Computer Human Interaction}, 22(6), article 33: 1--45.\\
\years{2015}F. Nunes, and G. Fitzpatrick (2015) ``Self-care Technologies and Collaboration", \emph{International Journal of Human Computer Interaction}, 31(12): 869--881.\\
\years{2012}A. Aguiar, F. Nunes, M. Silva, P. A. Silva, and D. Elias (2012) ``Leveraging electronic ticketing to provide personalised navigation in a public transport network", \emph{Intelligent Transportation Systems Transactions and Magazine}, 13(1): 213–220.


\subsection*{Full conference papers (peer-reviewed)}

\years{2019}A. Pereira, D. Folgado, F. Nunes, J. Almeida, I. Sousa (2019) ``Using Inertial Sensors to Evaluate Exercise Correctness in Electromyography-based Home Rehabilitation Systems'', \emph{Proc. of MEMEA 2019}\\
\years{2019}J. Silva, D. Gomes, F. Nunes, D. Moreira, J. Alves, A. Pereira, I. Sousa (2019) ``Position-independent Physical Activity Monitoring: Development and Comparison with Market Devices'', \emph{Proc. of MEMEA 2019}\\
\years{2018}F. Nunes, and G. Fitzpatrick (2018) ``Understanding the mundane nature of self-care: Ethnographic accounts of people living with Parkinson's'', \emph{Proc. of CHI 2018}, 402:1--402:15\\
\years{2018}F. Nunes, J. Ribeiro, C. Braga, P. Lopes``Supporting the Self-care Practices of Shift Workers'', \emph{Proc. of MUM 2018}, 71--81.\\
\years{2018}J. Silva, E. Oliveira, D. Moreira, F. Nunes, M. Caic, J. Madureira, Eduardo Pereira (2018) ``Design and evaluation of a fall prevention multiplayer game for senior care centres", \emph{Proc. of ICEC 2018}, 103--114.\\
\years{2013}P. Jordan, P. A. Silva, F. Nunes, and R. Oliveira (2013) ``mobileWAY – A System to Reduce the Feeling of Temporary Lonesomeness of Persons with Dementia and to Foster Inter-caregiver Collaboration", \emph{Proc. of HICSS 2013}, 2474--2483.\\
\years{2013}P. A. Silva, F. Nunes, A. Vasconcelos, M. Kerwin, R. Moutinho, and P. Teixeira (2013) ``Using the Smartphone Accelerometer to Monitor Fall Risk While Playing a Game: The Design and Usability Evaluation of Dance! Don't Fall", \emph{Proc. of HCII 2013}, 754--763.\\
\years{2012}F. Nunes, M. Kerwin, and P. A. Silva (2012) ``Design Recommendations for TV User Interfaces for Older Adults: Findings From the eCAALYX Project", \emph{Proc. of ASSETS 2012}, 41--48.\\
\years{2012}M. Kerwin, F. Nunes, and P. A. Silva (2012) ``Dance Don’t Fall -- Preventing Falls and Promoting Exercise at Home", \emph{Proc. of pHealth 2012}, 254--259.\\
\years{2012}A. Vasconcelos, P. A. Silva, J. Caseiro, F. Nunes, and L. F. Teixeira (2012) ``Designing Tablet-based Games for Seniors: the Example of Cogniplay, a Cognitive Gaming Platform", \emph{Proc. of Fun \& Games 2012}, 1--10.\\
\years{2010}P. A. Silva, and F. Nunes (2010) ``3 x 7 Usability Testing Guidelines for Older Adults", \emph{Proc. MEXIHC 2010}, 2: 1--8.\\
\years{2010}F. Nunes, P. A. Silva, and F. Abrantes (2010) ``Human-Computer Interaction and the Older Adult: an Example Using User Research and Personas", \emph{Proc. of PETRA 2010}, 49: 1--8.


\subsection*{Short conference papers (peer-reviewed)}

\years{2018}A. Vasconcelos, F. Nunes, A. Carvalho, C. Correia (2018) ``Mobile, Exercise-agnostic, Sensor-based Serious Games for Physical Rehabilitation at Home'', \emph{Proc. of TEI 2018}, 271--278.\\
\years{2018}V. Guimarães, F. Nunes (2018) ``A Wearable, Customizable, and Automated Auditory Cueing System to Stimulate Gait in Parkinson's", \emph{Proc. of PervasiveHealth 2018}.\\
\years{2018}A. Pereira, F. Nunes (2018) ``Physical Activity Intensity Monitoring of Hospital Workers using a Wearable Sensor", \emph{Proc. of PervasiveHealth 2018}.\\
\years{2018}R. Peixoto, J. Ribeiro, E. Pereira, F. Nunes, A. Pereira (2018) ``Designing the Smart Badge: A Wearable Device for Hospital Workers", \emph{Proc. of PervasiveHealth 2018}.\\
\years{2018}F. Aluvathingal, N. Verdezoto, and F. Nunes (2018) ``Exploring Challenges and Opportunities to Support People with Food Allergies to Find Safe Places for Eating Out", \emph{Proc. of 32nd British HCI Conference}.\\
\years{2017}F. Güldenpfennig, Ö.Subasi, F. Nunes, M. Urbanek (2017) ``UbiKit: Learning to Prototype for Tangible and Ubiquitous Computing", \emph{31st British HCI Conference}\\
\years{2015}F. Güldenpfennig, F. Nunes, and G. Fitzpatrick (2015) ``Proxycare: Integrating informal care into formal settings", \emph{Proc. of PervasiveHealth 2015}, 141--144.\\
\years{2011}T. Marques, F. Nunes, P. A. Silva, and R. Rodrigues (2011) ``Tangible Interaction on Tabletops for Elderly People", \emph{Proc. ICEC 2011}, pp. 440--443.\\
\years{2011}T. Sousa, P. Tenreiro, P. A. Silva, F. Nunes, and E. Rodrigues (2011) ``Cross-platform social web application for older adults with html 5", \emph{Proc. ICEC 2011}, pp. 375–-378.

\subsection*{Position papers (juried)}

\years{2019}F. Nunes (2019) ``From medicalized to mundane self-care technologies'', in \emph{Interactions}, 26(3), 67--69.\\
\years{2019}S. Y. Park, F. Nunes, A. Berry, A. Büyüktür, L. de Russis, M. Czerwinski, W. Seo (2019) ``Who Cares? Exploring the Concept of Care Networks for Designing Healthcare Technologies'', \emph{Proc. of ECSCW 2019}.\\
\years{2016}P. A. Silva, F. Nunes (2016) ``Preface for the special issue on fun and engaging computing technologies for health'', in \emph{Entertainment Computing}, 15: 41--42.\\
\years{2016}F. Nunes (2016) ``The medication reminder as enforcing a medicalised perspective on daily life'', in \emph{Book of abstracts of the 6th STS Italia Conference}, 58.\\
\years{2015}F. Nunes (2015) ``Designing Self-care Technologies for Everyday Life: A Practice Approach", \emph{Proc. of CHI EA 2015}, 215--218.\\
\years{2014}N. Verdezoto, F. Nunes, G. Fitzpatrick, E. Grönvall (2014) ``Preface to the Focus Section'', in \emph{Interaction Design and Architecture(s) Journal - IxD\&A}, 23.\\
\years{2013}F. Nunes (2013) ``Improving the Self-care of Parkinson’s Through Ubiquitous Computing", \emph{Proc. of Ubicomp Adjunct 2013}.\\
\years{2011}F. Nunes and, P. A. Silva (2011) ``The Smartphone -- A Mobile Companion for Older Adults", \emph{Proc. of Promoting and Supporting Healthy Living by Design Workshop at INTERACT 2011}, 41--43.\\
\years{2011}P. M. Teixeira, P. A. Silva, F. Nunes, and L. F. Teixeira (2011) ``Mover – Activity Monitor and Fall Detector for Android", \emph{Proc. of Mobile Wellness Workshop at MobileHCI 2011}.\\
\years{2010}F. Nunes, and P. A. Silva (2010) ``Fostering Wellness of Older Adults While Performing Usability Testing", \emph{Proc. of HCI4WELL Workshop at HCI2010}.\\
\years{2009}A. Aguiar, F. Nunes, M. Silva, and D. Elias (2009) ``Personal Navigator for a Public Transport System Using RFID Ticketing", \emph{Proc. of inMotion09 Workshop at Pervasive 2009}.

\subsection*{Invited presentations}

\years{09/09/2019}``Towards Mundane Personal Assistants'' Keynote at Ubicomp Workshop on Ubiquitous Personal Assistance, London, UK.\\
\years{03/05/2019}``Technology Assessment in Real Life'' at Escola Superior de Saúde, Porto, Portugal.\\ % II International Meeting of Medical Technology and Healthcare Business
\years{14/09/2015}``Understanding and Promoting the Creation of Patient Knowledge Online" at University of Trento \& FBK, Italy.\\
\years{17/08/2015}``How can technology help people improve their self-care? Supporting engagement in their clinical consultations" at IT University of Copenhagen, Denmark.\\
\years{17/08/2015}``Designing Self-care Technology for People with Parkinson’s: A Focus on Everyday Life" at University of Copenhagen, Denmark.\\
% \years{12/07/2012}``Design recommendations for TV user interfaces for older adults" at the Interactive Assistive Technologies for the Elderly Workshop in University of Aveiro, Portugal.\\
\years{06/05/2011}``eCAALYX project" at the course Multimodal Interfaces of University of Porto, Portugal.

\subsection*{Media mentions}

Mover was mentioned in the \href{http://www.jornaldenegocios.pt/empresas/detalhe/evitar_acidentes_com_idosos_pode_estar_agrave_distacircncia_de_um_telemoacutevel.html}{Jornal de Negócios} (30/04/2010) and \href{http://www.dn.pt/inicio/ciencia/interior.aspx?content_id=1581122&seccao=Tecnologia}{Diário de Notícias} (29/05/2010).\\
% Naviporto was news in \href{http://www.jn.pt/paginainicial/interior.aspx?content_id=1576870}{Jornal de Notícias} (24/05/2010) and \href{http://www.dn.pt/inicio/ciencia/interior.aspx?content_id=1581122&seccao=Tecnologia}{Diário de Notícias} (29/05/2010).\\
Smart Companion was described in \href{https://www.youtube.com/watch?v=nWqpXHaN5Is}{RTP} (01/08/2011), \href{https://www.youtube.com/watch?v=gIa2ZMeJ7MI}{Porto Canal}, and another time at \href{https://www.youtube.com/watch?v=miAXlLm2GSQ}{Porto Canal} (26/07/2012) when I was even interviewed.	

\section*{Languages}

Portuguese -- native\\
English -- proficient\\
Spanish -- fluent\\
French -- intermediate (DELF A4 certificate)\\
German -- intermediate (B1.1 certificate)\\

\section*{References}

Geraldine Fitzpatrick, TU Wien (\href{mailto:geraldine.fitzpatrick@tuwien.ac.at}{geraldine.fitzpatrick@tuwien.ac.at})\\
Ana Correia de Barros, Fraunhofer Portugal AICOS
(\href{mailto:ana.barros@fraunhofer.pt}{ana.barros@fraunhofer.pt})\\
Paula Alexandra Silva, University of Aveiro (\href{mailto:palexa@gmail.com}{palexa@gmail.com})\\
Nuno Correia, Universidade NOVA de Lisboa (\href{mailto:nmc@fct.unl.pt}{nmc@fct.unl.pt})\\


% Projects
% Mover http://www.youtube.com/watch?v=mut3Ghw3hF8

% \vfill{} % Whitespace before final footer

%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------

\begin{center}
{\scriptsize Last updated: \today\ } % Any final footer text such as a URL to the latest version of your CV, last updated date, compiled in XeTeX, etc
\end{center}

%----------------------------------------------------------------------------------------

\end{document}